Stable quantum memories with limited measurement

### 2017-07-20 IsingECC/manuscript_ising_ecc_final_3.tex
Add files via upload
Latest draft

@@

\begin{abstract}
 We demonstrate the existence of a finite temperature threshold for a 1D stabilizer code under an error correcting protocol that \CMH{requires only a} fraction of the syndrome measurements.  We sketch how this algorithm generalizes to higher dimensional stabilizer codes with string-like excitations, like the toric code. 
\end{abstract}

@@

%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\label{sec:Intro}
%%%%%%%%%%%%%%%%%%%%%%
 Quantum memories are an essential component for many quantum technologies, including quantum computing and quantum repeaters. In analogy to modern classical memories, one ideally wants a stable quantum memory that requires little or no active intervention and error correction. Unfortunately, no physical system that passively preserves quantum information indefinitely at finite temperatures and in an experimentally accessible number of dimensions is known \cite{Terhal:2015ks}. Instead, the operation of all known practical quantum memories require a combination of passive elements (i.e. dissipative cooling) and active measurement and correction cycles to keep quantum information protected.  In this work, we study the degree to which the amount of active measurement and correction can be reduced while maintaining quantum memory stability (our notion of stability, to be quantified later, corresponds to exponentially long lifetime for encoded states \MS{\sout{at} below} some finite threshold temperature). We develop a new decoding and correction protocol that enables one to trim the number of measurements to a fraction of the complete set of measurements normally considered, and still maintain quantum memory stability.

 We restrict our attention to quantum memories defined through stabilizer codes. For near term architectures, stabilizer codes\cite{Gottesman98} have emerged as the leading candidate for encoding quantum information and subsequent active error correction in quantum hardware, with small scale architectures actively being developed and deployed\cite{all the stabilizers}.  A tremendous amount of effort has gone into developing novel decoding schemes for stabilizer codes, particularly the toric code.  Different schemes often emphasize different decoding features, like efficient decoding\cite{Kovalev2013,Wang2009,Duclos-Cianci2010}, locality\cite{Breuckmann2016,Torlai2016,Harrington2004,Herold2014}, robustness to particular sorts of noise\cite{Novais2013,Bombin2012,Wootton2015}, or use of dissipation\cite{Freeman2016,Hutter2012a,Hutter2014,Fujii2014,Pedrocchi2013,Pedrocchi2011,Chesi2010a,Chesi2010b,Hamma2009,Herdman2010, Young2012,Weimer2010, Dengis2014, Kapit2015, Bardyn2015}.

 In previous work \cite{Freeman2014}, we analyzed the finite temperature dynamics of the toric code, verifying the well-known no-go theorems for the upper bound to the lifetime of the toric code at finite temperature\cite{Bravyi2009, Alicki2009a, Chesi2010b, Yoshida2011b, Hastings2011a, Landon-Cardinal2013, Temme2014, temme2015fast}.  Using this analysis, we were able to construct a measurement-free protocol for protecting the encoded qubits of the toric code \cite{Freeman2016}, but these protocols again were limited by the no-go theorems, and only provided a multiplicative constant increase to the lifetime.

 Building off this previous work, here we examine the extent to which a limited amount of measurement can increase the lifetime of stabilizer codes with string-like excitations.  In sum, we demonstrate an algorithm that, for any constant density of measurements for a stabilizer code with stringlike excitations undergoing dissipation at a fixed temperature, a threshold \MS{temperature?} can be achieved.  The threshold temperature scales with the amount of measurement used---fewer measurements result in a smaller threshold temperature, whereas more complete measurement raises the threshold temperature.  This tradeoff is commensurate with and complements what is known about decoding the stabilizer codes in the presence of \emph{noisy} \MS{Why is the emph environment underlined and not italicized}, but complete measurements\cite{Nickerson2016}.

 The remainder of the manuscript is structured as follows:  Section \ref{sec:stabfintemp} briefly reviews the theoretical tools used for performing simulation of stabilizer codes at finite temperature.  The content of this section is also expanded upon in refs \cite{Freeman2014,Freeman2016}.  Section \ref{sec:ecc_alg} includes the full description of our few-measurement algorithm, including a discussion of the expected low temperature error processes that cause the algorithm to fail, and a heuristic justification for the expectation of a \MS{\sout{threshold at low temperature} threshold temperature below which a stable quantum memory is feasible}.  Section \ref{sec:experiments} details our numerical investigations of our algorithm for the 1D Ising model.  Finally, Sec. \ref{sec:tc_alg} sketches how this algorithm could be generalized to higher dimensions, and Sec. \ref{sec:discussion} provides some concluding analysis and discussion.

@@

where, for the remainder of the manuscript, unless explicitly stated otherwise, we assume $\Delta=1$.  This is exactly the Hamiltonian version of the repetition stabilizer \emph{code}\cite{Freeman2016}.  Note that the terms $\sigma^i_z \sigma^{i+1}_z$ exactly correspond to the parity check stabilizer operators of the repetition code (see Table \ref{tab:code_vs_hamiltonian}).

\begin{table}
\begin{center}
  \begin{tabular}{ l | r }
    \hline
    Repetition Stabilizer Code & 1d Ising Stabilizer Hamiltonian \\ \hline
    Encoded States & Ground States \\ \hline
    Bit flip errors & Excited States \\ \hline
    Error correction via decoder & Same or via cooling \\ \hline
    \hline
  \end{tabular}
\end{center}
\caption{A short summary of the similarities and differences between the Ising model considered as a code versus as a hamiltonian.}
\label{tab:code_vs_hamiltonian}
\end{table}

@@

So long as less than half the system has had errors, a majority rule decoder that has access to measurements of the full set of stabilizers ${\sigma^i_z \sigma^{i+1}_z}$ will reliably be able to correctly remove errors.  When errors are completely independent (i.e., at very high temperature), we can define random variables $x_i=1$ when an error occurs on site $i$, and $0$ otherwise.  If these errors occur with probability $p$ on each spin, independently at random every error detection cycle, then Chernoff's bound gives an upper bound to the probability of an error in the encoded space, $P(\Sigma_i x_i \geq L/2) \leq \rm{exp}[-Lp\frac{\delta^2}{2+\delta}]$ for $\delta=1/2p-1$.  Thus, for complete measurement, errors in the encoded subspace are exponentially suppressed in system size, so long as the error rate is sufficiently small.

@@

Following Ref. \cite{Freeman2016}, we consider a simple local Ohmic, Markovian bath to model finite temperature effects.  This is modeled by the following master equation in Lindblad form:

\begin{align}
\dot{\rho }=\sum_{\omega }{2c_{\omega }\rho c^{\dagger }_\omega}-c^{\dagger }_{\omega }c_{\omega }\rho -\rho c^{\dagger }_{\omega }c_{\omega }, \label{eq:Lindblad}
\end{align}

for the density matrix $\rho$, with Lindblad operators $c_{\omega }$ chosen to take the form:

\begin{equation}
\left \{ c_\omega \right \} = \left \{ \sqrt{\gamma(0)} T_{b}, \sqrt{\gamma(1)} D^\dagger_{b}, \sqrt{\gamma(-1)} D_{b} \right\} 
\end{equation}
\MS{There is no $\omega$ dependence of the operators. What is b? Should we be saying $c_b$? Also, we don't say anywhere that we're assuming $\Delta=1$. In fact, let's keep the $\Delta$ in these expressions, since we refer to this energy scale in the simulations section.}
where $D_{b}$ dissipates a pair of defects,  $D^\dagger_{b}$ creates a pair of defects, $T_{b}$ translates a defect by one unit, and $\gamma(\cdot)$ is a rate function dependent on the details of the bath.  This bath is chosen to model the dynamics of local, single bit-flip errors.  In the Pauli basis, these operators take the following form.

\begin{align}
D^\dagger_{b}= &\frac{1}{4} \left(I \sigma_x I \right)\left(1+I \sigma_z \sigma_z\right)\left(1+ \sigma_z \sigma_z I\right) \notag \\
D_{b}= &\frac{1}{4} \left(I \sigma_x I \right)\left(1-I \sigma_z \sigma_z\right)\left(1-\sigma_z \sigma_z I\right) \notag \\
T_{b}= &\frac{1}{4} \left(I \sigma_x I \right)\left(1-I \sigma_z \sigma_z\right)\left(1+ \sigma_z \sigma_z I\right) \label{eq:LindbladDef}
\end{align}
\MS{Can we be more specific about the relationship between $b$ and the qubits that the Pauli's above act on?}

@@

Choosing $n=1$ corresponds to an Ohmic spectral density, which is the choice we make for the remainder of the manuscript.  With this choice, in the absence of any error correcting protocol, the 1D Ising model has a system size independent thermal \MS{logical} error rate given by\cite{Freeman2016}

@@

We define its bare lifetime to be $\Gamma_0^{-1}$.

@@

 The \CMH{\sout{vast}} majority of the error correction literature assumes an error model akin to an ``infinite temperature limit''.  More precisely, an array of qubits receives errors from some set of error operators ${E_i}$ independently at random with some probability $p$ every error correction cycle.  The threshold theorems state that there exists some critical error probability $p_c$ below which it is possible to return an error correcting code to its encoded state with unit probability for asymptotically large systems; e.g., for the toric code, $p_c\approx.11$ \MS{Need a citation here}.

 Contrariwise, thresholds at finite temperature are usually quoted in terms of a critical \emph{temperature}.  That is, there must exist some critical temperature $T_c$ below which codes can be reliably corrected.  Unfortunately, this definition obscures a great deal of physics---different choices of bath model can greatly affect the dynamics of the error processes, to the extent that a quoted ``critical temperature'' often implicitly specifies a choice of bath model.  Because different bath interactions can give rise to different system dynamics, the choice of bath also directly affects the strategy used for error correction.  For example, it is known that the toric code's threshold temperature is altered by considering a space-correlated bath rather than an uncorrelated one \cite{Novais2013}.

 The main consequence of choosing an Ohmic bath is that it sets the amplitude of the excitation hopping process.  That is, $\gamma(0)$ is determined by the $\omega \rightarrow 0$ limit of the spectral density of the bath, and for the Ohmic bath taking the $\omega\rightarrow0$ limit of  Eq. \ref{eq:gammadef} yields $\gamma(0) \sim T$. 
Ultimately, this means that the hopping rate of domain walls is controlled by this choice of bath model. At finite temperatures, this introduces correlations into the patterns of errors that effect the system, and so it is no longer possible to talk about an ``independent error probability per site''. 
In contrast to the behavior of $\gamma(0)$, 
the other operationally important feature of the bath, the ratio of defect creation and annihilation rates, is set by detailed balance to Boltzmann-like scaling (i.e., $\gamma(1)/\gamma(-1) = \exp(-1/T)$), and is independent of the choice of bath spectrum.

 In the most extreme case, at sufficiently low temperature, pairs of neighboring defects are most often immediately dissipated by the bath upon creation.  However, if a pair creation is followed by pair hopping event -- i.e., a $D^\dagger_{b}$ followed by a $T_{b}$ -- the error can no longer be immediately dissipated by the local action of the bath.  Subsequently the defects will undergo a one-dimensional random walk, and topologically non-trivial random walks will cause uncorrectable logical errors.

@@

In this section, we sketch a new algorithm which reliably dissipates defects in the 1D Ising model below a threshold temperature, which we determine numerically.  The primary technical innovation of this algorithm, and its generalization to quantum memories based on any stabilizer Hamiltonian, is that it does not require measurement of the complete set of stabilizer operators for a given stabilizer code---only a fixed subset.  We assume that the system is subject to periodic measurements on periodically spaced measurement ``patches'', that measurement readout and processing occurs much faster than any system timescale, and that the system is subject to a thermal bath as described in Sec. \ref{sec:Defs}.

\begin{figure}
\begin{center}
\scalebox{1}{\includegraphics[width=1.0\columnwidth]{detect_swap.pdf}}
\end{center}
\caption{This cartoon illustrates the ``centering'' procedure for detected defects on a unit cell.  Spin variables are in gray, and domain wall variables are in blue (no defect present) and red (defect present).  When a defect is detected on a measurement patch (blue box), it is swapped to the center of the measurement patch via the $\rm{DSWAP}$ operator (black arrows).  The defect immediately adjacent to it is also swapped onto the measurement patch so as not to pull apart defect pairs that would have otherwise dissipated.  Measurement patch lengthscale $\lambda$ indicated by arrow on top, and unit cell lengthscale $\lambda$ indicated by arrow on bottom. \MS{The measurement fraction is defined as $m\equiv \lambda_m/\lambda$.}}
\label{fig:detect_swap}
\end{figure}

The algorithm can be summarized in fives steps:

1. Measure stabilizers on patches, keeping record of the age of defects that are already on patches, as well as defect locations.

2. Perform ``centering'' on patches with defects (see \figref{fig:detect_swap}), based on centering protocol introduced in Ref. \cite{Freeman2016}.

3. Calculate probability of fusion (explicitly given in Eq. \ref{eq:bayes_simple}) for all pairs of measured defects residing on the measurement sites.

@@

5. Repeat

Step 2 encourages defects to remain localized at measurement patches.  This centering protocol can be performed entirely unitarily by the $DSWAP$ operator, which takes the following form in the Pauli basis,
\begin{align}
\rm{DSWAP} &= \frac{1}{2} \left(III + I\sigma_x I + \sigma_z I \sigma_z - \sigma_z \sigma_x \sigma_z \right)
\end{align}
\MS{Can we be more specific about which qubits these Pauli operators act on? i.e. are the the qubits at the boundary of a measurement patch? Does this operator take the same form regardless of the size of the measurement patch, or is this specifically for $\lambda_m=3$?}

The centering process aids the probability of fusion calculation by ensuring that the coordinates and measurement times are representative of when and where defects are actually created.  If defects escape from measurement patches, then upon being measured again, the time recorded by the measurement patch now underestimates how old the defect actually is, biasing the probability estimate.  This centering operation greatly reduces the probability of defect escape.  This systematic underestimate \MS{do you mean: "Any remaining underestimate"} of defect lifetimes can be fixed by a more elaborate record keeping protocol (See Appendix \ref{sec:appendix_fix_long_errors}).

@@

To calculate this probability, we proceed via Bayes rule: 
\begin{align}
\label{eq:bayes}
&P(d_1:d_2 | d_1^{x_1,t_1} \wedge d_2^{x_2,t_2}) = \\ \notag
&\frac{P(d_1^{x_1,t_1} \wedge d_2^{x_2,t_2} | d_1:d_2) P(d_1 : d_2)}{P(d_1^{x_1,t_1}\wedge d_2^{x_2,t_2})}
\end{align}
The individual terms on the right hand side of equation \ref{eq:bayes} are straightforward to interpret.  $d_i^{x_i,t_i}$ indicates a defect \MS{\sout{residing on measurement patch $i$ with} residing on a measurement patch centered on} spacetime coordinate $x_i,t_i$.  $P(d_1^{x_1,t_1} \wedge d_2^{x_2,t_2} | d_1:d_2)$ represents the probability that two measured defects would be at $(x_1,t_1)$ and $(x_2,t_2)$ given that they are indeed a pair. \CMH{$P(d_1 : d_2)$ represents the probability that two measured defects, $d_1$ and $d_2$, are in fact a pair.  Finally, $P(d_1^{x_1,t_1}\wedge d_2^{x_2,t_2})$ is the probability that two defects are measured, one at $(x_1,t_1)$, and the other at $(x_2,t_2)$. }

\CMH{\sout{This} $P(d_1^{x_1,t_1} \wedge d_2^{x_2,t_2} | d_1:d_2)$} can be related to the probability that a one dimensional diffusion process with diffusion constant $D$ will perform an excursion with a displacement $|x_2-x_1|$ or greater in a time $t_2 - t_1$; \textit{i.e.,} will perform an excursion that can reach measurement patches at $x_1$ and $x_2$. Explicitly,
\begin{align}
\label{eq:bayesformula}
&P(d_1^{x_1,t_1} \wedge d_2^{x_2,t_2} | d_1:d_2) \\ \notag
&= 1-2\int_{0}^{|x_2-x_1|} dx \frac{1}{2\pi D |t_2-t_1|} {\rm exp}\bigg(-\frac{|x_2-x_1|^2}{2 D |t_2-t_1|}\bigg) \\ \notag 
&= 1 - {\rm erf}\bigg(\frac{|x_2-x_1|}{2\sqrt{D |t_2 - t_1|}}\bigg) 
\end{align}
For our analysis, we will choose $D\propto \gamma_0$.  The exact correspondence between $D$ and $\gamma_0$ depends on the details of the error correction algorithm itself, so, in practice, we treat the constant of proportionality as an empirically tuned parameter.  Furthermore, we approximate any detected defects as arising from a pair that was created an equal distance between the measurement patches at locations $x_1$ and $x_2$ for the purposes of calculating the probability in Eq. \ref{eq:bayesformula}.

\CMH{\sout{$P(d_1 : d_2)$ represents the probability that two measured defects, $d_1$ and $d_2$, are in fact a pair.  Finally, $P(d_1^{x_1,t_1}\wedge d_2^{x_2,t_2})$ is the probability that two defects are measured, one at $(x_1,t_1)$, and the other at $(x_2,t_2)$.}}  As we discuss in Appendix \ref{sec:bayesdecoder}, \CMH{\sout{these} the remaining two} factors are not as important for the decoding scheme as \MS{the likelihood term} in Eq. \ref{eq:bayesformula}.  In practice, we find that using the expression from Eq. \ref{eq:bayesformula} alone is sufficient to provide resilient error correction.  We defer further discussion to the appendix.

@@

  In this section, we derive the \MS{logical} error rate for a simple error model.  While this error model does not account for the complete error dynamics of the full 1D Ising model in the presence of our protocol, we argue how it nonetheless serves as \MS{\sout{an upper bound} a worst-case approximation} to the true error dynamics.  Finally, we sketch how this protocol provides a threshold for any finite density of measurements.

>>>>

\let\oldemph\emph
\renewcommand*{\emph}[1]{{\it {#1}}}

@@

\begin{abstract}
 We demonstrate the existence of a finite temperature threshold for a 1D stabilizer code under an error correcting protocol that requires only a fraction of the syndrome measurements.  Below the threshold temperature, encoded states have exponentially long lifetimes, as demonstrated by numerical and analytical arguments.  We sketch how this algorithm generalizes to higher dimensional stabilizer codes with string-like excitations, like the toric code. 
\end{abstract}

@@

%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\label{sec:Intro}
%%%%%%%%%%%%%%%%%%%%%%
 Quantum memories are an essential component for many quantum technologies, including quantum computing and quantum repeaters. In analogy to modern classical memories, one ideally wants a stable quantum memory that requires little or no active intervention and error correction. Unfortunately, no physical system that passively preserves quantum information indefinitely at finite temperatures and in an experimentally accessible number of dimensions is known \cite{Terhal2015ks}. Instead, the operation of all known practical quantum memories require a combination of passive elements (i.e. dissipative cooling) and active measurement and correction cycles to keep quantum information protected.  In this work, we study the degree to which the amount of active measurement and correction can be reduced while maintaining quantum memory stability (our notion of stability, to be quantified later, corresponds to exponentially long lifetime for encoded states below some finite threshold temperature). We develop a new decoding and correction protocol that enables one to trim the number of measurements to a fraction of the complete set of measurements normally considered, and still maintain quantum memory stability.

 We restrict our attention to quantum memories defined through stabilizer codes. For near term architectures, stabilizer codes\cite{Gottesman98} have emerged as the leading candidate for encoding quantum information and subsequent active error correction in quantum hardware, with small scale architectures actively being developed and deployed\cite{Knill2001,Takita2017,Chiaverini2004,Corcoles2015}.  A tremendous amount of effort has gone into developing novel decoding and correction schemes for stabilizer codes, particularly the toric code.  Different schemes often emphasize different decoding features, like efficient decoding\cite{Kovalev2013,Wang2009,Duclos-Cianci2010}, locality\cite{Breuckmann2016,Torlai2016,Harrington2004,Herold2014}, robustness to particular sorts of noise\cite{Novais2013,Bombin2012,Wootton2015}, or use of dissipation\cite{Freeman2017,Hutter2012a,Hutter2014,Fujii2014,Pedrocchi2013,Pedrocchi2011,Chesi2010a,Chesi2010b,Hamma2009,Herdman2010, Young2012,Weimer2010, Dengis2014, Kapit2015, Bardyn2015}.

 In previous work \cite{Freeman2014}, we analyzed the finite temperature dynamics of the toric code, verifying the well-known no-go theorems for the upper bound to the lifetime of the toric code at finite temperature\cite{Bravyi2009, Alicki2009a, Chesi2010b, Yoshida2011b, Hastings2011a, Landon-Cardinal2013, Temme2014, temme2015fast}.  Using this analysis, we were able to construct a measurement-free protocol for protecting the encoded qubits of the toric code \cite{Freeman2017}, but these protocols again were limited by the no-go theorems, and only provided a multiplicative constant increase to the lifetime.

 Building off this previous work, here we examine the extent to which a limited amount of measurement can increase the lifetime of stabilizer codes with string-like excitations.  In sum, we demonstrate an algorithm that, for any constant density of measurements for a stabilizer code with stringlike excitations undergoing dissipation at a fixed temperature, exhibits a threshold temperature, below which exponentially long lifetimes can be achieved in the encoded space.  The threshold temperature scales with the amount of measurement used---fewer measurements result in a smaller threshold temperature, whereas more complete measurement raises the threshold temperature.  This tradeoff is commensurate with and complements what is known about decoding the stabilizer codes in the presence of \emph{noisy}, but complete measurements\cite{Nickerson2016}.

 The remainder of the manuscript is structured as follows:  Section \ref{sec:stabfintemp} briefly reviews the theoretical tools used for performing simulation of stabilizer codes at finite temperature.  The content of this section is also expanded upon in refs \cite{Freeman2014,Freeman2017}.  Section \ref{sec:ecc_alg} includes the full description of our limited measurement algorithm, including a discussion of the expected low temperature error processes that cause the algorithm to fail, and a heuristic justification for the expectation of a threshold temperature below which a stable quantum memory is feasible.  Section \ref{sec:experiments} details our numerical investigations of our algorithm for the 1D Ising model.  Finally, Sec. \ref{sec:tc_alg} sketches how this algorithm could be generalized to higher dimensions, and Sec. \ref{sec:discussion} provides some concluding analysis and discussion.

@@

where, for the remainder of the manuscript, unless explicitly stated otherwise, we assume $\Delta=1$.  This is exactly the Hamiltonian version of the repetition stabilizer \emph{code}\cite{Freeman2017}.  Note that the terms $\sigma^i_z \sigma^{i+1}_z$ correspond exactly to the parity check stabilizer operators of the repetition code (see Table \ref{tab:code_vs_hamiltonian}).

\begin{table}
\begin{center}
  \begin{tabular}{ l | r }
    \hline
    Repetition Stabilizer Code & 1d Ising Stabilizer Hamiltonian \\ \hline
    Encoded States & Ground states \\ \hline
    Bit flip errors & Excited states \\ \hline
    Decoding and error correction & Identical or by cooling \\ \hline
    \hline
  \end{tabular}
\end{center}
\caption{A short summary of the similarities and differences between the Ising model considered as a code (left panel) versus as a hamiltonian (right panel).}
\label{tab:code_vs_hamiltonian}
\end{table}

@@

As long as less than half the system has had errors, a majority rule decoder that has access to measurements of the full set of stabilizers ${\sigma^i_z \sigma^{i+1}_z}$ will reliably be able to correctly identify and remove errors.  When errors are completely independent (i.e., at very high temperature), we can define random variables $x_i=1$ when an error occurs on site $i$, and $0$ otherwise.  If these errors occur with probability $p$ on each spin, independently at random every error detection cycle, then Chernoff's bound gives an upper bound to the probability of an error in the encoded space, $P(\Sigma_i x_i \geq L/2) \leq \rm{exp}[-Lp\frac{\delta^2}{2+\delta}]$ for $\delta=1/2p-1$.  Thus, for complete measurement, errors in the encoded subspace are exponentially suppressed in system size, so long as the error rate is sufficiently small.

@@

Following Ref. \cite{Freeman2017}, we consider a simple local Ohmic, Markovian bath to model finite temperature effects.  This is modeled by the following master equation in Lindblad form:

\begin{align}
\dot{\rho }=\sum_{i}{2c_{i}\rho c^{\dagger }_i}-c^{\dagger }_{i}c_{i}\rho -\rho c^{\dagger }_{i}c_{i}, \label{eq:Lindblad}
\end{align}

Here $\rho$ is the density matrix, with Lindblad operators $c_{i}$ chosen to take the form:

\begin{equation}
\left \{ c_i (\Delta) \right \} = \left \{ \sqrt{\gamma(0)} T_{i}, \sqrt{\gamma(\Delta)} D^\dagger_{i}, \sqrt{\gamma(-\Delta)} D_{i} \right\} 
\end{equation}
where $T_{b}$ translates a defect by one unit, $D^\dagger_{b}$ creates a pair of defects, $D_{b}$ dissipates a pair of defects, and $\gamma(\cdot)$ is a rate function dependent on the details of the bath.  This bath is chosen to model the dynamics of local, single bit-flip errors.  In the Pauli basis, these operators take the following form.

\begin{align}
D^\dagger_{i}= &\frac{1}{4} \left(I \sigma_x I \right)\left(1+I \sigma_z \sigma_z\right)\left(1+ \sigma_z \sigma_z I\right) \notag \\
D_{i}= &\frac{1}{4} \left(I \sigma_x I \right)\left(1-I \sigma_z \sigma_z\right)\left(1-\sigma_z \sigma_z I\right) \notag \\
T_{i}= &\frac{1}{4} \left(I \sigma_x I \right)\left(1-I \sigma_z \sigma_z\right)\left(1+ \sigma_z \sigma_z I\right), \label{eq:LindbladDef}
\end{align}

By convention, we define $i$ to index the first qubit in these operators.

@@

where $n=1$ corresponds to an Ohmic spectral density, which is the choice we make for the remainder of the manuscript.  With this choice, in the absence of any error correcting protocol, it can be shown that the 1D Ising model has a system size independent thermal logical error rate given by\cite{Freeman2017}

@@

We define the bare lifetime of qubits evolving under the 1D Ising model Hamiltonian in contat with an Ohmic thermal bath to be $\Gamma_0^{-1}$.

@@

 The majority of the error correction literature assumes an error model akin to an ``infinite temperature limit''.  More precisely, an array of physical qubits receives errors from some set of error operators ${E_i}$ independently at random with some probability $p$ during every error correction cycle.  The threshold theorems state that there exists some critical error probability $p_c$ below which it is possible to return an error correcting code to its encoded state with unit probability for asymptotically large systems; e.g., for the toric code, $p_c\approx.109$ \cite{Wang2009}.

 In contrast, thresholds at finite temperature are usually quoted in terms of a critical \emph{temperature}.  That is, there must exist some critical temperature $T_c$ below which codes can be reliably corrected.  Unfortunately, this definition obscures a great deal of physics---different choices of bath model can greatly affect the dynamics of the error processes, to the extent that a quoted ``critical temperature'' often implicitly specifies a choice of bath model.  Because different bath interactions can give rise to different system dynamics, the choice of bath also directly affects the strategy used for error correction.  For example, it is known that the toric code's threshold temperature is altered by considering a space-correlated bath rather than an uncorrelated one \cite{Novais2013}.

 The main consequence of choosing an Ohmic bath is that it sets the amplitude of the excitation hopping process.  That is, $\gamma(0)$ is determined by the $\omega \rightarrow 0$ limit of the spectral density of the bath, and for the Ohmic bath taking the $\omega\rightarrow0$ limit of  Eq. \ref{eq:gammadef} yields $\gamma(0) \sim T$. 
Ultimately, this means that the hopping rate of domain walls is controlled by this choice of bath model. At finite temperatures, this introduces correlations into the patterns of errors that effect the system, and so it is no longer possible to talk about an ``independent error probability per site''. 
In contrast to the behavior of $\gamma(0)$, 
the other operationally important feature of the bath, the ratio of defect creation and annihilation rates, is set by detailed balance to Boltzmann-like scaling (i.e., $\gamma(\Delta)/\gamma(-\Delta) = \exp(-\Delta/T)$), and is independent of the choice of bath spectrum.

 In the most extreme case, at sufficiently low temperature, pairs of neighboring defects are most often immediately dissipated by the bath upon creation via a $D_b$ operator.  However, if a pair creation is followed by a pair hopping event -- i.e., a $D^\dagger_{b}$ followed by a $T_{b}$ -- the error can no longer be immediately dissipated by the local action of the bath.  Subsequently the defects will undergo a one-dimensional random walk, and topologically non-trivial random walks will cause uncorrectable logical errors.

@@

In this section, we sketch a new algorithm which reliably removes errors in the 1D Ising model below a threshold temperature, which we determine numerically.  The primary technical innovation of this algorithm, and its generalization to quantum memories based on any stabilizer Hamiltonian, is that it does not require measurement of the complete set of stabilizer operators for a given stabilizer code---only a fixed subset.  We assume $i)$ that the system is subject to periodic measurements on periodically spaced measurement ``patches'', $ii)$ that measurement readout and processing occurs much faster than any system timescale, and $iii)$ that the system is subject to a thermal bath as described in Sec. \ref{sec:Defs}.

\begin{figure}
\begin{center}
\scalebox{1}{\includegraphics[width=1.0\columnwidth]{detect_swap.pdf}}
\end{center}
\caption{This cartoon illustrates the ``centering'' procedure for detected defects on a unit cell.  Spin variables are in gray, and domain wall variables are in blue (no defect present) and red (defect present).  When a defect is detected on a measurement patch (blue box), it is swapped to the center of the measurement patch via the $\rm{DSWAP}$ operator (black arrows).  The defect immediately adjacent to it is also swapped onto the measurement patch so as not to pull apart defect pairs that would have otherwise dissipated.  Measurement patch lengthscale $\lambda$ indicated by arrow on top, and unit cell lengthscale $\lambda$ indicated by arrow on bottom. The measurement fraction is defined as $m\equiv \lambda_m/\lambda$.}
\label{fig:detect_swap}
\end{figure}

The algorithm can be summarized in five steps:

1. Measure stabilizers on patches, keeping record of the age of defects that are already on patches---i.e., the amount of time a defect is continuously detected on a patch---as well as defect locations.

2. Perform ``centering'' on patches with defects (see \figref{fig:detect_swap}), based on centering protocol introduced in Ref. \cite{Freeman2017}.

3. Calculate probability of fusion (explicitly given in Eq. \ref{eq:bayes_simple}) for all pairs of measured defects residing on the measurement sites.  This probability serves as an estimate for whether two defects should be paired or not for the purposes of error correction.

@@

5. Repeat steps $1-4$.

Step 2 encourages defects to remain localized at measurement patches.  This centering protocol can be performed entirely unitarily by the $\rm{DSWAP}$ operator, which takes the following form in the Pauli basis,
\begin{align}
\rm{DSWAP}_i &= \frac{1}{2} \left(III + I\sigma_x I + \sigma_z I \sigma_z - \sigma_z \sigma_x \sigma_z \right)
\end{align}

where $i$ indexes the location of the first qubit being acted upon by the operator by convention.

If a domain wall exists either between the first and second qubit or the second and third qubit, then the \rm{DSWAP} operator exchanges those domain walls.  If there are no domain walls, it acts as the identity.  By concatenating a sequence of \rm{DSWAP}s, i.e. $\rm{DSWAP}_i \rm{DSWAP}_{i+1} \rm{DSWAP}_{i+2} ...$, domain walls can be shuttled to the center of the measurement patch for efficient tracking.

The centering process, illustrated in Fig. \ref{fig:detect_swap}, aids the probability of fusion calculation by ensuring that the coordinates and measurement times are representative of when and where defects are actually created.  If defects escape from measurement patches, then upon being measured again, the time recorded by the measurement patch now underestimates how old the defect actually is, biasing the probability estimate.  This centering operation greatly reduces the probability of defect escape.  Any remaining underestimate of defect lifetimes can be fixed by a more elaborate record keeping protocol (See Appendix \ref{sec:appendix_fix_long_errors}).

@@

To calculate this probability, we proceed via Bayes rule: 
\begin{align}
\label{eq:bayes}
&P(d_1:d_2 | d_1^{x_1,t_1} \wedge d_2^{x_2,t_2}) = \\ \notag
&\frac{P(d_1^{x_1,t_1} \wedge d_2^{x_2,t_2} | d_1:d_2) P(d_1 : d_2)}{P(d_1^{x_1,t_1}\wedge d_2^{x_2,t_2})}
\end{align}
The individual terms on the right hand side of equation \ref{eq:bayes} are straightforward to interpret.  $d_i^{x_i,t_i}$ indicates a defect  residing on a measurement patch centered on spacetime coordinate $x_i,t_i$.  $P(d_1^{x_1,t_1} \wedge d_2^{x_2,t_2} | d_1:d_2)$ represents the probability that two measured defects would be at $(x_1,t_1)$ and $(x_2,t_2)$ given that they are indeed a pair. $P(d_1 : d_2)$ represents the probability that two measured defects, $d_1$ and $d_2$, are in fact a pair.  Finally, $P(d_1^{x_1,t_1}\wedge d_2^{x_2,t_2})$ is the probability that two defects are measured, one at $(x_1,t_1)$, and the other at $(x_2,t_2)$.

$P(d_1^{x_1,t_1} \wedge d_2^{x_2,t_2} | d_1:d_2)$ can be related to the probability that a one dimensional diffusion process with diffusion constant $D$ will perform an excursion with a displacement $|x_2-x_1|$ or greater in a time $t_2 - t_1$, \textit{i.e.,} will perform an excursion that can reach measurement patches at $x_1$ and $x_2$. Explicitly,
\begin{align}
\label{eq:bayesformula}
&P(d_1^{x_1,t_1} \wedge d_2^{x_2,t_2} | d_1:d_2) \\ \notag
&= 1-2\int_{0}^{|x_2-x_1|} dx \frac{1}{2\pi D |t_2-t_1|} {\rm exp}\bigg(-\frac{|x_2-x_1|^2}{2 D |t_2-t_1|}\bigg) \\ \notag 
&= 1 - {\rm erf}\bigg(\frac{|x_2-x_1|}{2\sqrt{D |t_2 - t_1|}}\bigg) 
\end{align}
For our analysis, we will choose $D\propto \gamma_0$.  The exact correspondence between $D$ and $\gamma_0$ depends on the details of the error correction algorithm itself, so, in practice, we treat the constant of proportionality as an empirically tuned parameter.  Furthermore, we approximate any detected defects as arising from a pair that was created an equal distance between the measurement patches at locations $x_1$ and $x_2$ for the purposes of calculating the probability in Eq. \ref{eq:bayesformula}.

 As we discuss in Appendix \ref{sec:bayesdecoder}, the remaining two factors are not as important for the decoding scheme as the likelihood term in Eq. \ref{eq:bayesformula}.  In practice, we find that using the expression from Eq. \ref{eq:bayesformula} alone is sufficient to provide resilient error correction.  We defer further discussion to the appendix.

@@

  In this section, we discuss parameter regime in which we expect the error correcting algorithm to perform well.  We then derive the logical error rate for a simple error model, under some simplifying assumptions about the error dynamics.  While this error model does not account for the complete error dynamics of the full 1D Ising model in the presence of our protocol, we argue how it nonetheless serves as a worst-case approximation to the true error dynamics.  Finally, we describe how this protocol provides a threshold for any finite density of measurements.

 In this section, we detail the approximations and rate assumptions that are necessary for the error correcting algorithm to perform well.  The primary approximations made are concerning \textbf{(1)} fast defect detection, \textbf{(2)} accurate pairing, \textbf{(3)} defects escaping measurement patches, and \textbf{(4)} defect interactions.

 \textbf{(1)}. If defects are produced in between measurement patches faster than they are detected, then this algorithm cannot in principle correct errors.  Thus, we require that the characteristic diffusion time for defects in the bulk to migrate to a measurement patch, $\gamma_0^{-1}(\lambda_b)^2$, where $\lambda_b=\lambda-\lambda_m$, to be much shorter than the characteristic timescale over which a pair of defects is created in the bulk, $\gamma_0^{-1} \exp{\Delta/T}$.  Thus, working at low temperature ensures the validity of this approximation.
